### 2024-01-27 tesis_Ashish/Chapter4/chapter4.tex
update 27 Jan

\newpage
\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/afterglow_correction_factor_1lsblock_315690_2.png}
\caption[Run 315690 Afterglow Background]{%                                                                                                                                                                                                                                                                                                
 Raw and corrected PCC for all bunch crossings.
}
\label{fig:af_change_veto}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/afterglow_correction_factor_1lsblock_315690_3.png}
\caption[Run 315690 Afterglow Background]{%
  Afterglow scale factor for one 50 lumi section block in run 315690 for the final module veto.
}
\label{fig:af_change_veto}
\end{figure}

>>>>

\newpage
\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/afterglow_correction_factor_1lsblock_315690_2.png}
\caption[Run 315690 PCC without and with afterglow correction]{%                                                                                                                                                                                                                                                                                                
 Raw and corrected PCC for all bunch crossings.
}
\label{fig:af_change_veto}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/afterglow_correction_factor_1lsblock_315690_3.png}
\caption[Run 315690 afterglow scale factor]{%
  Afterglow scale factor for one 50 lumi section block in run 315690 for the final module veto.
}
\label{fig:af_change_veto}
\end{figure}
